### 2019-08-27 paper_00_fluiddyn_meta/article.tex

Web related activities alone account for at least 5\% of GDP in the USA and the
European Union\footnote{See the report by Internet Association titled
\href{https://internetassociation.org/reports/refreshing-understanding-internet-economy-ia-report/}
{``Refreshing Our Understanding of the Internet Economy''}}.
% \cite{hooton_christopher_refreshing_2017}.
A huge amount of money (and work) is invested on the related technologies. We
are familiar with the most prominent companies involved in this dynamics
(Google, Facebook, etc.), but there are also several smaller and sometimes
lesser known organizations.  Most of these companies base part of their work on
the open-source paradigm contributing to open-source languages, libraries,
software and operating systems, while also using them --- a win-win situation
for both the corporations and the community.
%
This has lead to deep changes in software engineering, with a massive use of
open-source methods and tools, for example
\href{https://en.wikipedia.org/wiki/Distributed_version_control}{distributed
version control systems (DVCS)} and web-based source development platforms.

>>>>

Web related activities alone account for at least 5\% of GDP in the USA and the
European Union\footnote{See the report by Internet Association titled
{``Refreshing Our Understanding of the Internet Economy''}
\url{https://internetassociation.org/reports/refreshing-understanding-internet-economy-ia-report/}
}.
% \cite{hooton_christopher_refreshing_2017}.
A huge amount of money (and work) is invested on the related technologies. We
are familiar with the most prominent companies involved in this dynamics
(Google, Facebook, etc.), but there are also several smaller and sometimes
lesser known organizations.  Most of these companies base part of their work on
the open-source paradigm contributing to open-source languages, libraries,
software and operating systems, while also using them --- a win-win situation
for both the corporations and the community.
%
This has lead to deep changes in software engineering, with a massive use of
open-source methods and tools, for example
\href{https://en.wikipedia.org/wiki/Distributed_version_control}{distributed
version control systems (DVCS)} and web-based source development platforms.

### 2019-08-27 paper_02_fluidsim/article.tex
Fix Table 1 in fluidsim paper

\begin{table}[h]
\centering
\begin{tabular}{l p{8cm}}
  \toprule
  Cluster & Beskow (Cray XC40 system with Aries interconnect) \\
  CPU &  Intel Xeon CPU E5--2695v4, 2.1GHz \\
  Operating System & SUSE Linux Enterprise Server 11, Linux Kernel 3.0.101\\
  No.\ of cores per nodes used & 32 \\
  Maximum no.\ of nodes used & 32 (2D cases), 256 (3D cases) \\
  Compilers & CPython 3.6.5, Intel C++ Compiler (\pack{icpc}) 18.0.0 \\
  Python packages & \fluidpack{dyn} 0.2.3, \fluidpack{fft} 0.2.3,
  \fluidpack{sim} 0.2.1, \pack{numpy} (OpenBLAS) 1.14.2, \pack{Cython} 0.28.1,
  \pack{mpi4py} 3.0.0, \pack{pythran} 0.8.5 \\

@@

\begin{figure}[htp]
\centering
\includegraphics[width=\linewidth]{./tmp/fig_compare_with_ns3d}
\caption{Comparison of the execution times for a 3D case (128$^3$, 10 time steps)
between NS3D (blue bars) and \codeinline{fluidsim.solvers.ns3d} (yellow bars).
%
The first two bars correspond to the total time and the others to the main tasks
in terms of time consumption, namely FFT, Runge-Kutta 4, curl, vector product and
``projection''. }
\label{fig:compare:with:ns3d}
\end{figure}

Fig.~\ref{fig:compare:with:ns3d} presents a more detailed comparison between NS3D
(blue bars) and \fluidpack{sim} (yellow bars).
%
The total elapsed times is mainly spent in five tasks: FFTs, Runge-Kutta 4, curl,
vector product and ``projection''. The times spent to perform these tasks are
compared for the two codes.

>>>>

\begin{table}[h]
\centering
\begin{tabular}{l p{7cm}}
  \toprule
  Cluster & Beskow (Cray XC40 system with Aries interconnect) \\
  CPU &  Intel Xeon CPU E5--2695v4, 2.1GHz \\
  Operating System & SUSE Linux Enterprise Server 11, Linux Kernel 3.0.101\\
  No.\ of cores per nodes used & 32 \\
  Maximum no.\ of nodes used & 32 (2D cases), 256 (3D cases) \\
  Compilers & CPython 3.6.5, Intel C++ Compiler (\pack{icpc}) 18.0.0 \\
  Python packages & \fluidpack{dyn} 0.2.3, \fluidpack{fft} 0.2.3,
  \fluidpack{sim} 0.2.1, \pack{numpy} (OpenBLAS) 1.14.2, \pack{Cython} 0.28.1,
  \pack{mpi4py} 3.0.0, \pack{pythran} 0.8.5 \\

@@

\begin{figure}[htp]
\centering
\includegraphics[width=\linewidth]{./tmp/fig_compare_with_ns3d}
\caption{Comparison of the execution times for a 3D case (128$^3$, 10 time steps)
between NS3D (blue / dark bars) and \codeinline{fluidsim.solvers.ns3d} (yellow / light bars).
%
The first two bars correspond to the total time and the others to the main tasks
in terms of time consumption, namely FFT, Runge-Kutta 4, curl, vector product and
``projection''. }
\label{fig:compare:with:ns3d}
\end{figure}

Fig.~\ref{fig:compare:with:ns3d} presents a more detailed comparison between NS3D
(blue / dark bars) and \fluidpack{sim} (yellow / light bars).
%
The total elapsed times is mainly spent in five tasks: FFTs, Runge-Kutta 4, curl,
vector product and ``projection''. The times spent to perform these tasks are
compared for the two codes.
